Monster or Lambda?  A likelihood analysis

### 2023-03-21 inst/monster_vs_lambda.Rmd
reworking of limits

```{r,label=ttrydefflikefvc,cache=TRUE}
Mval <- seq(from=0.0,to=0.3,len=5)
lval <- seq(from=0.1,to=5,len=5)
jj <- as.matrix(expand.grid(M=Mval,lam=lval))
L <- apply(jj,1,like2)
```

```{r}
L <- matrix(L,length(Mval),length(lval))
L <- L-max(L)
L
L <- pmax(L,-10)
L
Mval
lval
contour(Mval,lval,L,xlab='M',ylab='lambda')
filled.contour(Mval,lval,L,xlab='M',ylab='lambda')
```

>>>>

```{r,label=ttrydefflikefvc,cache=TRUE}
Mval <- seq(from=0.0,to=0.65,len=15)
lval <- seq(from=0.2,to=5,by = 0.4) # we need lambda=1 (this is the null)
jj <- as.matrix(expand.grid(M=Mval,lam=lval))
options(use_alabama = FALSE)
L <- apply(jj,1,like2)
```

```{r}
options(digits=2)
options(width=150)
L <- matrix(L,length(Mval),length(lval))
L <- L-max(L)
rownames(L) <- paste("M = ",round(Mval,2))
colnames(L) <- paste("lam=",lval,sep="")
L
L <- pmax(L,-9)
L
Mval
lval
contour(Mval,lval,L,xlab='M',ylab='lambda')
abline(h=1,lwd=5)
abline(v=0,lwd=5)
filled.contour(Mval,lval,L,xlab='M',ylab='lambda')
matplot(Mval,L,type='b')
matplot(lval,t(L),type='b')
```
